---
title: "Executive Summary"
subtitle: "Reproducible OHDSI methodological demonstration"
bibliography: references.bib
---

```{r}
source("R/plots.R", local = FALSE)
reporting_inputs <- validate_reporting_inputs(".")
primary <- reporting_inputs$outcome_analysis_summary
subgroups <- reporting_inputs$subgroup_analysis_summary
sensitivity <- reporting_inputs$sensitivity_analysis_summary
propensity <- reporting_inputs$propensity_score_summary
```

## Study question

This synthetic-data demonstration compares new use of Celecoxib with new use of
Diclofenac for gastrointestinal hemorrhage during days 1 through 30 after
treatment initiation.

> Adjusted observational association under the stated design assumptions.

This is not clinical evidence, regulatory evidence, or a drug-safety conclusion.

## Main result

The matched ATT analysis included
`r format(primary$targetSubjectCount[[1L]], big.mark = ",")` Celecoxib initiators
and
`r format(primary$comparatorSubjectCount[[1L]], big.mark = ",")` Diclofenac
initiators, with `r primary$eventCount[[1L]]` total events.

The odds ratio was
`r format_estimate_ci(primary$estimate[[1L]], primary$ciLower[[1L]], primary$ciUpper[[1L]])`
using `r primary$varianceEstimator[[1L]]`.

The confidence interval includes 1.0. The result is not interpreted as benefit,
harm, equivalence, safety, or absence of an association.

## Diagnostics

```{r}
diagnostic_table <- data.frame(
  Diagnostic = c(
    "Matched pairs",
    "Covariates evaluated",
    "Residual imbalances",
    "Maximum absolute SMD after matching",
    "Balance threshold"
  ),
  Value = c(
    propensity$matched_pair_count[[1L]],
    propensity$covariate_count[[1L]],
    propensity$unbalanced_after_count[[1L]],
    sprintf("%.3f", propensity$maximum_absolute_smd_after[[1L]]),
    sprintf("%.1f", propensity$balance_threshold[[1L]])
  ),
  check.names = FALSE
)
knitr::kable(diagnostic_table)
```

Residual imbalance remained after matching; adjustment is not treated as proof
that confounding was removed.

## Prespecified additional analyses

All five sensitivity scenarios are retained. Their odds-ratio range was
`r sprintf("%.2f", min(sensitivity$estimate))` to
`r sprintf("%.2f", max(sensitivity$estimate))`, with no scenario selected as
preferred after reviewing the results.

The age subgroup `>=65` was `NOT_ESTIMABLE` because no subjects were available.
This result is reported rather than suppressed or replaced.

## Limitations

Eunomia is synthetic or sample data. Residual and unmeasured confounding,
misclassification, incomplete observation, limited overlap, sparse outcomes,
missing data, and model instability remain possible. The short fixed risk
window and binary logistic model restrict interpretation.

The report uses only aggregate artifacts, does not access a database, and does
not recompute the study estimates.
