---
title: "Signal to Evidence: Reproducible OHDSI Study Report"
subtitle: "Celecoxib versus Diclofenac and 30-day gastrointestinal hemorrhage"
bibliography: references.bib
---

```{r}
source("R/plots.R", local = FALSE)
reporting_inputs <- validate_reporting_inputs(".")
primary <- reporting_inputs$outcome_analysis_summary
subgroups <- reporting_inputs$subgroup_analysis_summary
sensitivity <- reporting_inputs$sensitivity_analysis_summary
propensity <- reporting_inputs$propensity_score_summary
cohorts <- reporting_inputs$cohort_counts
effect_plot_data <- prepare_effect_estimate_plot_data(reporting_inputs)
balance_plot_data <- prepare_balance_plot_data(reporting_inputs)
```

## Scope and interpretation

This report is a reproducible methodological demonstration using aggregate Eunomia
OMOP outputs. It is not clinical evidence, regulatory evidence, or a drug-safety
conclusion.

> Adjusted observational association under the stated design assumptions.

The report does not make a causal claim and does not describe either treatment as
safe or unsafe.

## Frozen study design

```{r}
design_table <- data.frame(
  Element = c(
    "Target",
    "Comparator",
    "Outcome",
    "Primary risk window",
    "Estimand",
    "Adjustment",
    "Effect measure",
    "Uncertainty"
  ),
  Specification = c(
    "Celecoxib",
    "Diclofenac",
    "Gastrointestinal hemorrhage",
    "Day 1 through day 30 after index",
    "ATT",
    "1:1 propensity-score matching with 5% preference-score trimming",
    "Odds ratio",
    "Matched-set cluster-robust CR1 with a 95% Wald confidence interval"
  ),
  check.names = FALSE
)
knitr::kable(design_table)
```

## Cohort construction

```{r}
cohort_display <- data.frame(
  Group = c("Celecoxib", "Diclofenac", "Outcome cohort"),
  Subjects = c(
    cohorts$target_subject_count[[1L]],
    cohorts$comparator_subject_count[[1L]],
    cohorts$outcome_subject_count[[1L]]
  ),
  Entries = c(
    cohorts$target_entry_count[[1L]],
    cohorts$comparator_entry_count[[1L]],
    cohorts$outcome_entry_count[[1L]]
  ),
  check.names = FALSE
)
knitr::kable(cohort_display)
```

## Propensity-score adjustment and balance

The matching procedure retained
`r format(propensity$matched_target_count[[1L]], big.mark = ",")` target subjects
and `r format(propensity$matched_comparator_count[[1L]], big.mark = ",")`
comparator subjects in
`r format(propensity$matched_pair_count[[1L]], big.mark = ",")` matched pairs.

The maximum absolute standardized mean difference changed from
`r sprintf("%.3f", propensity$maximum_absolute_smd_before[[1L]])` before
adjustment to
`r sprintf("%.3f", propensity$maximum_absolute_smd_after[[1L]])` after
adjustment. The prespecified threshold was
`r sprintf("%.1f", propensity$balance_threshold[[1L]])`.
Residual imbalance remained in
`r propensity$unbalanced_after_count[[1L]]` covariates; therefore matching is not
presented as proof that confounding was eliminated.

```{r}
balance_top <- head(balance_plot_data, 40L)
balance_labels <- abbreviate(balance_top$covariateName, minlength = 35L)
balance_positions <- seq_len(nrow(balance_top))
plot(
  balance_top$absoluteSmd,
  balance_positions,
  pch = 19,
  yaxt = "n",
  xlab = "Absolute standardized mean difference",
  ylab = "",
  main = "Largest absolute balance diagnostics"
)
axis(2, at = balance_positions, labels = balance_labels, las = 2, cex.axis = 0.55)
abline(v = propensity$balance_threshold[[1L]], lty = 2)
```

## Primary adjusted association

The primary matched analysis included
`r format(primary$subjectCount[[1L]], big.mark = ",")` subjects and
`r format(primary$eventCount[[1L]], big.mark = ",")` events.

The odds ratio was
`r format_estimate_ci(primary$estimate[[1L]], primary$ciLower[[1L]], primary$ciUpper[[1L]])`.
The model converged and used
`r primary$varianceEstimator[[1L]]`.

> `r primary$interpretation[[1L]]`

The confidence interval includes 1.0. This result is not interpreted as evidence
of benefit, harm, equivalence, or absence of an association.

## Prespecified subgroup analyses

```{r}
subgroup_display <- data.frame(
  Subgroup = paste(subgroups$subgroupType, subgroups$subgroupLevel, sep = ": "),
  Status = subgroups$estimabilityStatus,
  Subjects = subgroups$subjectCount,
  Events = subgroups$eventCount,
  Estimate = ifelse(
    subgroups$estimabilityStatus == "ESTIMABLE",
    sprintf(
      "%.2f (%.2f to %.2f)",
      subgroups$estimate,
      subgroups$ciLower,
      subgroups$ciUpper
    ),
    subgroups$estimabilityReason
  ),
  Residual_imbalances = subgroups$unbalancedCovariateCount,
  check.names = FALSE
)
knitr::kable(subgroup_display)
```

The age subgroup `>=65` is retained as `NOT_ESTIMABLE`; it is not removed,
replaced, or pooled after reviewing the results.

## Prespecified sensitivity analyses

```{r}
sensitivity_display <- data.frame(
  Scenario = sensitivity$scenarioId,
  Changed_parameter = sensitivity$changedParameter,
  Adjustment = sensitivity$adjustmentMethod,
  Washout_days = sensitivity$washoutDays,
  Risk_window = paste0(
    sensitivity$riskWindowStartDays,
    "-",
    sensitivity$riskWindowEndDays
  ),
  Subjects = sensitivity$subjectCount,
  Events = sensitivity$eventCount,
  Estimate = sprintf(
    "%.2f (%.2f to %.2f)",
    sensitivity$estimate,
    sensitivity$ciLower,
    sensitivity$ciUpper
  ),
  check.names = FALSE
)
knitr::kable(sensitivity_display)
```

All five prespecified scenarios are reported without selecting a preferred
result based on magnitude, direction, confidence interval, or statistical
significance.

```{r}
estimable_effects <- effect_plot_data[
  effect_plot_data$estimabilityStatus == "ESTIMABLE" &
    is.finite(effect_plot_data$estimate) &
    is.finite(effect_plot_data$ciLower) &
    is.finite(effect_plot_data$ciUpper),
  ,
  drop = FALSE
]
plot_positions <- rev(seq_len(nrow(estimable_effects)))
plot(
  estimable_effects$estimate,
  plot_positions,
  log = "x",
  xlim = range(c(estimable_effects$ciLower, estimable_effects$ciUpper)),
  pch = 19,
  yaxt = "n",
  xlab = "Odds ratio (log scale)",
  ylab = "",
  main = "Primary, subgroup, and sensitivity estimates"
)
segments(
  estimable_effects$ciLower,
  plot_positions,
  estimable_effects$ciUpper,
  plot_positions
)
axis(
  2,
  at = plot_positions,
  labels = estimable_effects$label,
  las = 2,
  cex.axis = 0.65
)
abline(v = 1, lty = 2)
```

## Limitations

Eunomia is synthetic or sample demonstration data and does not represent a
clinical population. The analysis remains vulnerable to residual and unmeasured
confounding, exposure and outcome misclassification, incomplete observation,
limited overlap, sparse events, missing data, and model instability.

The post-match balance threshold was not met for every covariate. A short fixed
risk window and a binary logistic model further restrict interpretation.
Engineering feasibility, model convergence, and observed balance do not
establish exchangeability or clinical validity.

## Reproducibility

The report reads only version-controlled aggregate CSV artifacts. It does not
connect to a database, load row-level records, or recompute cohorts or effect
estimates. Reporting is rendered with Quarto [@quarto2026] from the frozen
OHDSI/OMOP workflow [@ohdsi2026; @omopcdm2026].
